Plot Figures for McDuffie et al., 2023 (those generated in R)

### 2023-05-11 analysis/Manuscript/Paper_RFigures.Rmd
Updates to R figure files

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/CCD-CSIB/GitHub/Code/MOMM-RFT")
#setwd("~/CCD-CSIB/GitHub/Code/MOMM-RFT")
```

```{r libraries, include = FALSE}
library('tidyverse')
library('reshape2')
library('patchwork')
library('RColorBrewer')
library('maps')
library('mapproj')
library('arrow')
library('readxl')
library('zoo')
#library('Rfast')
```

@@

#Define BemMAP years and create dataframes
Model.years<-c(2020,2025,2030,2035,2040,2050,2060,2070,2080,2090,2100)
s1Data_methane <- data.frame(Model.years)
s1Data_ozone <- data.frame(Model.years)

#Read in the globally averaged mean O3 response data
# Generated by /analaysis/Manuscript/BenMAP/Inputs/Generate AQ Surfaces for BenMAP.R
All.mean.results <- read.csv(file.path(Input,"AQ Surfaces","Mean_Pulse_Data.csv"))

@@

#chloropleth of world
p5 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = TotalResults),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("Total Deaths",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(0,100000),
                       #breaks= c(0,100,1000,5000,10000,20000,40000,60000,100000),
                       breaks= c(0,100,1000,10000,100000),
                       #n.breaks = 6,
                       label=scales::comma)+#,
                       #guide =  guide_colorbar(nbin=10))+

                       #guides() (fill= guide_colorbar(even.steps) = FALSE
  #scale_fill_continuous(name="Total Mortality (deaths per 100K)",
  #                      low="darkblue",
  #                      high="lightblue",
  #                      limits=c(0,70),
  #                      na.value='gray')+
  theme_void()+
  theme(legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  #guide(c)

@@

#mortality rate
p6 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, 
                                      fill = MeanMortalityRate),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("Respiratory Mortality Rates",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(min(MergedData$MeanMortalityRate, na.rm=TRUE),
                                max(MergedData$MeanMortalityRate, na.rm=TRUE)),
                       #breaks= c(0,100,1000,5000,10000,20000,40000,60000,100000),
                       #breaks= c(0,100,1000,10000,100000),
                       #n.breaks = 6,
                       #label=scales::comma)+
                       labels = c('Minimum','','','','','','Maximum'))+

@@

#avg response
p8 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = AvgResponse),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(min(MergedData$AvgResponse, na.rm=TRUE),
                                max(MergedData$AvgResponse, na.rm=TRUE)),
                       #breaks= c(0,100,1000,5000,10000,20000,40000,60000,100000),
                       #breaks= c(0,100,1000,10000,100000),
                       #n.breaks = 6,
                       #label=scales::comma)+
                       labels = c('Minimum','','','','','','Maximum'))+
  theme_void()+
  ggtitle(expression(paste('c) Average Ozone Response (pptv ', O[3],"/", "ppbv ",CH[4],')')))+
  theme(legend.position = 'bottom')+
  theme(legend.key.width = unit(2,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  theme(plot.title = element_text(size = 20))+
  #guides(col = guide_legend(override.aes = list(shape = 15, size = 10)))+
  coord_map(projection = 'mercator',xlim=c(-180,180),ylim = c(-55,80))
p8

@@

ggsave(plot = p, filename = 
         file.path(Plots,'Plots',paste0('Relative_2020_CombMaps_',MODEL,'.png')),width = 9,height = 15)

ggsave(plot = p5, filename = 
         file.path(Plots,'Plots',paste0('Relative_2020_DeathsPerCapMaps_',MODEL,'.png')),width = 9,height = 5)
p5
```

```{r, damagesbar}

#create bar graph of damages by region

## FIgure 2c

countryresults <-
  #read_csv(file.path('Results',"Country Results Interpolated Mortality Annual Undiscounted Damages.csv"),
   #        col_types = cols())
   read_csv(file.path('Results',"npd_country_damage_transformation_NoCessation.csv"),
           col_types = cols())

globalresults <-
  read_csv(file.path('Results',"npd_global_damage_transformation_NoCessation.csv"),
           col_types = cols())

@@

cResultslong <- countryresults %>%
  group_by_at(.vars = c('Model','SuperRegion','discount.rate')) %>%
  summarise_at(c('mean','2.5%','97.5%'),sum,na.rm=T) %>%
  ungroup() %>%
  arrange(desc(mean)) %>%
  #mutate(damages = damages/275e6,
  #       damages_2_5 = damages_2_5/275e6,
  #       damages_97_5 = damages_97_5/275e6) %>% #convert to per mt CH4 (not discounted)
  filter(Model =='MMM') %>%
  #select(-c('TotalResults','TotalPct2_5','TotalPct97_5','Model')) %>%
    rbind(globalresults)

@@

# cResultslong <- reshape2::melt(cResultslong, id="SuperRegion")
# cResultslong$Model.years <- strtoi(str_replace(cResultslong$variable, 'X',''))
# globalMMM <- globalResultslong[globalResultslong$Model == 'MMM - Mean AQS',]
# globalMMM$SuperRegion <- 'Global'
# globalMMM <- globalMMM %>%
#   select(-c('Model'))
# cResultslong <- rbind(cResultslong, globalMMM)

#cResultslong <- cResultslong %>%
#  group_by_at(c("COUNTRY","Model.years")) %>%
#  arrange(desc(value)) %>%
#  mutate(COUNTRY = factor(COUNTRY, levels=c(

  reg_i <- cResultslong %>% 
  group_by_at(.vars=c("SuperRegion")) %>% 
  #filter(Model.years == 2020) %>%
  summarize_at(.vars=c("mean"),sum,na.rm=T) %>%
  ungroup %>% arrange((mean)) %>%
  distinct(SuperRegion)

@@

  p1 <-  ggplot(cResultslong, aes(x=SuperRegion, y=mean))+
        geom_linerange(aes(x=SuperRegion,ymin=`2.5%`, ymax=`97.5%`,group=discount.rate),
                       color = 'lightgray',size=1,
                       position = position_dodge(0.8))+
        geom_point(aes(color = discount.rate), position = position_dodge(0.8),size=2)+
        coord_flip()+
        scale_color_brewer('Discount Rate',palette = 'Spectral',direction=-1)+
        scale_x_discrete(labels = function(x) str_wrap(x,width=30))+
        scale_y_continuous(limits=c(0,3000), label = scales::dollar)+
        #scale_linetype_manual(values=c(rep("solid",9),"solid","solid"))+
        #scale_colour_manual(values=c("black",brewer.pal(7,"Spectral")))+
        #scale_size_manual(values=c(rep(1,5),1.5,1))+
        xlab("")+ylab("$(2020)/mT" ~CH[4])+
        ggtitle(paste0('Net Present Damages per metric ton methane \nby GBD Super Region'))+
        theme_minimal()+
        theme(legend.position = c(0.7,0.4),
              legend.title=element_text(size=16), 
              legend.text=element_text(size=16))+
        theme(axis.text = element_text(size=16),
              axis.title = element_text(size=16))#+
        #geom_text(data=means, 
        #    aes(y=means, x=SuperRegion, group=discount.rate, 
        #        label=paste0('$', round(means, 2)), vjust=-1.5),
        #    #position = position_dodge(1.3),
        #    color    = 'grey20',
        #    size     = 4) 
        #scale_x_continuous(breaks=seq(2020,2100,10))
        #scale_y_continuous(limits=c(0,11500))
p1

p2 <-  cResultslong %>%
        filter(discount.rate == '2.0% Ramsey') %>%
        ggplot(aes(x=SuperRegion, y=mean,fill = SuperRegion))+
        geom_bar(stat = 'identity', position = 'dodge',width=0.6)+
        geom_pointrange(aes(x=SuperRegion,ymin=`2.5%`, ymax=`97.5%`),
                        position = position_dodge(width=0.2),size=0.3,alpha=0.8)+#errobar,width = 0.4)+
        coord_flip()+
        scale_fill_brewer(palette = 'Spectral',direction=-1)+
        scale_x_discrete(labels = function(x) str_wrap(x,width=30))+
        scale_y_continuous(limits=c(0,3000), label = scales::dollar)+
        #scale_linetype_manual(values=c(rep("solid",9),"solid","solid"))+
        #scale_colour_manual(values=c("black",brewer.pal(7,"Spectral")))+
        #scale_size_manual(values=c(rep(1,5),1.5,1))+
        xlab("")+ylab("$(2020)/mT" ~CH[4])+
        ggtitle(paste0('Damages per metric ton methane \nby GBD Super Region'))+
        theme_minimal()+
        theme(legend.position = 'none')+#c(0.7,0.3))+
        theme(axis.text = element_text(size=16),
              axis.title = element_text(size=16))+
        geom_text(data=means%>%filter(discount.rate == '2.0% Ramsey'),
            aes(y=means, x=SuperRegion,
                label=paste0('$', round(means, 2)), vjust=-0.35,hjust = -0.35),
            #position = position_dodge(1.3),
            color    = 'grey20',
            size     = 6)
        #scale_x_continuous(breaks=seq(2020,2100,10))
        #scale_y_continuous(limits=c(0,11500))
p2

ggsave(plot = p1, filename = 
         file.path('Results','Global BenMAP WebTool','Plots','npd_country_bar_discount.png'),width = 10,height = 5)
ggsave(plot = p2, filename = 
         file.path('Results','Global BenMAP WebTool','Plots','npd_country_bar_Ram2.png'),width = 10,height = 5)

@@

#
```{r globaldiscountbars}

#create bar graph of damages by region

Results <- file.path('Results')
globalresults <-
  read_csv(file.path(Results,"npd_global_damage_transformation_woutCessation.csv"),
           col_types = cols())

## ordering of central rate for alpha transparency
globalresults$discount.rate <- factor(globalresults$discount.rate, 
                                  levels=c('3.0% CDR','2.0% CDR',
                                          "3.0% Ramsey","2.5% Ramsey", 
                                          "2.0% Ramsey", "1.5% Ramsey" ))

## function for labels
means = globalresults %>% 
  group_by(discount.rate) %>% 
  summarise(means=mean) %>% 
  mutate(across(c('means'), ~ signif(.,3)))

p1 <-  ggplot(globalresults, aes(x=discount.rate, y=mean))+
        geom_point(stat = 'identity')+
        geom_pointrange(aes(x=discount.rate,ymin=`2.5%`, ymax=`97.5%`),size=0.3,alpha=0.8)+#errobar,width = 0.4)+
        coord_flip()+
        scale_fill_brewer(palette = 'Spectral',direction=-1)+
        scale_x_discrete(labels = function(x) str_wrap(x,width=30))+
        scale_y_continuous(limits=c(500,3500), label = scales::dollar)+
        #scale_linetype_manual(values=c(rep("solid",9),"solid","solid"))+
        #scale_colour_manual(values=c("black",brewer.pal(7,"Spectral")))+
        #scale_size_manual(values=c(rep(1,5),1.5,1))+
        xlab("")+ylab("$(2020)/mT" ~CH[4])+
        ggtitle(paste0('Global NPD per metric ton methane'))+
        theme_minimal()+
        theme(legend.position = 'none')+
        theme(axis.text = element_text(size=16),
              axis.title = element_text(size=16))+
        geom_text(data=means, 
            aes(y=means, x=discount.rate, group=discount.rate, 
                label=paste0('$', round(means, 2)), vjust=-1.5),
            #position = position_dodge(1.3),
            color    = 'grey20',
            size     = 4) 
        #scale_x_continuous(breaks=seq(2020,2100,10))
        #scale_y_continuous(limits=c(0,11500))
p1

ggsave(plot = p1, filename = 
         file.path(Results,'Global BenMAP WebTool','Plots','Global_NPD_by_discounting.png'),width = 10,height = 5)

```{r tornado}

#create a tornado plot with npd results from:
#1. different GCMs (created from monetization code?)
#2. BenMAP (created from monetization code?)
#3. Disocunting (created from monetization code)
#3. BenMAP socioeconomic scenarios (from methane-ozone RFT)
#4. NOx (**)

#Read in 
Results <- file.path('Results')
globalresults <-
  read_csv(file.path(Results,"npd_global_damage_transformation_NoCessation.csv"),
           col_types = cols())
Results2 <- file.path('C:/Users/emcduf01','OneDrive - Environmental Protection Agency (EPA)',
                      'Documents','CCD-CSIB','GitHub','Code','MOMM-RFT','output',
                      'npd_global_rff_means_MMM.csv')
rft_results <- read_csv(Results2, col_types = cols())
nox_results1 <- file.path('C:/Users/emcduf01','OneDrive - Environmental Protection Agency (EPA)',
                      'Documents','CCD-CSIB','GitHub','Code','MOMM-RFT','output',
                      'npd','npd_global_rff_means_NOx_1_MMM.csv')
nox_results1 <- read_csv(nox_results1, col_types = cols())%>%
  mutate(NOx = '1')
nox_results5 <- file.path('C:/Users/emcduf01','OneDrive - Environmental Protection Agency (EPA)',
                      'Documents','CCD-CSIB','GitHub','Code','MOMM-RFT','output',
                      'npd','npd_global_rff_means_NOx_0.5_MMM.csv')
nox_results5 <- read_csv(nox_results5, col_types = cols())%>%
  mutate(NOx = '0.5')
nox_results15 <- file.path('C:/Users/emcduf01','OneDrive - Environmental Protection Agency (EPA)',
                      'Documents','CCD-CSIB','GitHub','Code','MOMM-RFT','output',
                      'npd','npd_global_rff_means_NOx_1.5_MMM.csv')
nox_results15 <- read_csv(nox_results15, col_types = cols()) %>%
  mutate(NOx = '1.5')
nox_total_results <- rbind(nox_results1,nox_results5,nox_results15)

#gcm_results <- globalresults %>% filter(discount.rate == '2.0% Ramsey')
#gcm_results$diff <- gcm_results$mean - gcm_results$mean[gcm_results$Model=='MMM']
#gcm_results_min <- gcm_results %>% slice_min(diff)
#gcm_results_max <- gcm_results %>% slice_max(diff)

@@

#calulate the absolute difference
val_col <- val_col - globalresults$mean[globalresults$Model=='MMM' & globalresults$discount.rate=='2.0% Ramsey']

@@

ggsave(plot = p1, filename = 
         file.path(Results,'Global BenMAP WebTool','Plots','Global Uncertainty.png'),width = 10,height = 5)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/CCD-CSIB/GitHub/Code/MOMM-RFT")
```

```{r libraries, include = FALSE}
library('tidyverse')
library('reshape2')
library('patchwork')
library('RColorBrewer')
library('maps')
library('mapproj')
library('arrow')
library('readxl')
library('zoo')
```

@@

#Define BenMAP years and create dataframes
Model.years<-c(2020,2025,2030,2035,2040,2050,2060,2070,2080,2090,2100)
s1Data_methane <- data.frame(Model.years)
s1Data_ozone <- data.frame(Model.years)

#Read in the globally averaged mean O3 response data
# Generated by /analysis/Manuscript/BenMAP/Inputs/Generate AQ Surfaces for BenMAP.R
All.mean.results <- read.csv(file.path(Input,"AQ Surfaces","Mean_Pulse_Data.csv"))

@@

#chloropleth of world
p5 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = TotalResults),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("Total Deaths",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(0,100000),
                       breaks= c(0,100,1000,10000,100000),
                       label=scales::comma)+
  theme_void()+
  theme(legend.spacing.y = unit(.5,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+

@@

#mortality rate
p6 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, 
                                      fill = MeanMortalityRate),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("Respiratory Mortality Rates",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(min(MergedData$MeanMortalityRate, na.rm=TRUE),
                                max(MergedData$MeanMortalityRate, na.rm=TRUE)),
                       labels = c('Minimum','','','','','','Maximum'))+

@@

#avg response
p8 <- ggplot() +
  geom_polygon(data = MergedData, aes(x=long, y = lat, group=group, fill = AvgResponse),
               color = 'black',linewidth=0.15)+
  scale_fill_fermenter("",
                       n.breaks=9,
                        type = 'seq',
                       direction = -1,
                        palette = "Spectral",
                        na.value='lightgray',
                       limits=c(min(MergedData$AvgResponse, na.rm=TRUE),
                                max(MergedData$AvgResponse, na.rm=TRUE)),
                       labels = c('Minimum','','','','','','Maximum'))+
  theme_void()+
  ggtitle(expression(paste('c) Average Ozone Response (pptv ', O[3],"/", "ppbv ",CH[4],')')))+
  theme(legend.position = 'bottom')+
  theme(legend.key.width = unit(2,'cm'),
        legend.text = element_text(size=12),
        legend.title = element_text(size=13))+
  theme(plot.title = element_text(size = 20))+
  coord_map(projection = 'mercator',xlim=c(-180,180),ylim = c(-55,80))
p8

@@

ggsave(plot = p, filename = 
         file.path(Plots,paste0('Relative_2020_CombMaps_',MODEL,'.png')),width = 9,height = 15)

ggsave(plot = p5, filename = 
         file.path(Plots,paste0('Relative_2020_DeathsPerCapMaps_',MODEL,'.png')),width = 9,height = 5)
```

## Figure 2c and SX

barchart of NPD values by region, central case and by discount rate
```{r, damagesbar}

Plots <- file.path(getwd(), 'analysis','Manuscript','Plots')
inputs <- file.path(getwd(),'analysis','Manuscript','BenMAP','Outputs')
countryresults <-
   read_csv(file.path(inputs,"npd_country_damage_transformation_woutCessation.csv"),
           col_types = cols())

globalresults <-
  read_csv(file.path(inputs, "npd_global_damage_transformation_woutCessation.csv"),
           col_types = cols())

@@

cResultslong <- countryresults %>%
  group_by_at(.vars = c('Model','SuperRegion','discount.rate')) %>%
  summarise_at(c('mean','2.5%','97.5%'),sum,na.rm=T) %>%
  ungroup() %>%
  arrange(desc(mean)) %>%
  filter(Model =='MMM') %>%
  rbind(globalresults)

@@

  reg_i <- cResultslong %>% 
  group_by_at(.vars=c("SuperRegion")) %>% 
  summarize_at(.vars=c("mean"),sum,na.rm=T) %>%
  ungroup %>% arrange((mean)) %>%
  distinct(SuperRegion)

@@

  # Figure SX

  p1 <-  ggplot(cResultslong, aes(x=SuperRegion, y=mean))+
        geom_linerange(aes(x=SuperRegion,ymin=`2.5%`, ymax=`97.5%`,group=discount.rate),
                       color = 'lightgray',size=1,
                       position = position_dodge(0.8))+
        geom_point(aes(color = discount.rate), position = position_dodge(0.8),size=2)+
        coord_flip()+
        scale_color_brewer('Discount Rate',palette = 'Spectral',direction=-1)+
        scale_x_discrete(labels = function(x) str_wrap(x,width=30))+
        scale_y_continuous(limits=c(0,3000), label = scales::dollar)+
        xlab("")+ylab("$(2020)/mT" ~CH[4])+
        ggtitle(paste0('Net Present Damages per metric ton methane \nby GBD Super Region'))+
        theme_minimal()+
        theme(legend.position = c(0.7,0.4),
              legend.title=element_text(size=16), 
              legend.text=element_text(size=16))+
        theme(axis.text = element_text(size=16),
              axis.title = element_text(size=16))
# Figure 2c
p2 <-  cResultslong %>%
        filter(discount.rate == '2.0% Ramsey') %>%
        ggplot(aes(x=SuperRegion, y=mean,fill = SuperRegion))+
        geom_bar(stat = 'identity', position = 'dodge',width=0.6)+
        geom_pointrange(aes(x=SuperRegion,ymin=`2.5%`, ymax=`97.5%`),
                        position = position_dodge(width=0.2),size=0.3,alpha=0.8)+#errobar,width = 0.4)+
        coord_flip()+
        scale_fill_brewer(palette = 'Spectral',direction=-1)+
        scale_x_discrete(labels = function(x) str_wrap(x,width=30))+
        scale_y_continuous(limits=c(0,3000), label = scales::dollar)+
        xlab("")+ylab("$(2020)/mT" ~CH[4])+
        ggtitle(paste0('Damages per metric ton methane \nby GBD Super Region'))+
        theme_minimal()+
        theme(legend.position = 'none')+#c(0.7,0.3))+
        theme(axis.text = element_text(size=16),
              axis.title = element_text(size=16))+
        geom_text(data=means%>%filter(discount.rate == '2.0% Ramsey'),
            aes(y=means, x=SuperRegion,
                label=paste0('$', round(means, 2)), vjust=-0.35,hjust = -0.35),
            color    = 'grey20',
            size     = 6)
p2

ggsave(plot = p1, filename = 
         file.path(Plots,'npd_country_bar_discount.png'),width = 10,height = 5)
ggsave(plot = p2, filename = 
         file.path(Plots,'Fig2c.png'),width = 10,height = 5)

@@

Extra
```{r globaldiscountbars}

# #create bar graph of damages by region
# Plots <- file.path(getwd(), 'analysis','Manuscript','Plots')
# inputs <- file.path(getwd(),'analysis','Manuscript','BenMAP','Outputs')
# countryresults <-
#    read_csv(file.path(inputs,"npd_country_damage_transformation_woutCessation.csv"),
#            col_types = cols())
# 
# globalresults <-
#   read_csv(file.path(inputs, "npd_global_damage_transformation_woutCessation.csv"),
#            col_types = cols())
# 
# Results <- file.path('Results')
# globalresults <-
#   read_csv(file.path(Results,"npd_global_damage_transformation_woutCessation.csv"),
#            col_types = cols())
# 
# globalresults <- 
#   globalresults  %>%
#   group_by_at(.vars = c('Model','discount.rate')) %>%
#   arrange(desc(mean)) %>%
#   filter(Model =='MMM') %>%
#   mutate(SuperRegion = 'Global')%>%
#   filter(discount.rate %in% 
#            c('1.5% Ramsey', '2.0% Ramsey', '2.5% Ramsey', "3.0% Ramsey",'2.0% CDR','3.0% CDR'))
# 
# ## ordering of central rate for alpha transparency
# globalresults$discount.rate <- factor(globalresults$discount.rate, 
#                                   levels=c('3.0% CDR','2.0% CDR',
#                                           "3.0% Ramsey","2.5% Ramsey", 
#                                           "2.0% Ramsey", "1.5% Ramsey" ))
# 
# 
# ## function for labels
# means = globalresults %>% 
#   group_by(discount.rate) %>% 
#   summarise(means=mean) %>% 
#   mutate(across(c('means'), ~ signif(.,3)))
# 
# 
# 
# p1 <-  ggplot(globalresults, aes(x=discount.rate, y=mean))+
#         geom_point(stat = 'identity')+
#         geom_pointrange(aes(x=discount.rate,ymin=`2.5%`, ymax=`97.5%`),size=0.3,alpha=0.8)+#errobar,width = 0.4)+
#         coord_flip()+
#         scale_fill_brewer(palette = 'Spectral',direction=-1)+
#         scale_x_discrete(labels = function(x) str_wrap(x,width=30))+
#         scale_y_continuous(limits=c(500,3500), label = scales::dollar)+
#         #scale_linetype_manual(values=c(rep("solid",9),"solid","solid"))+
#         #scale_colour_manual(values=c("black",brewer.pal(7,"Spectral")))+
#         #scale_size_manual(values=c(rep(1,5),1.5,1))+
#         xlab("")+ylab("$(2020)/mT" ~CH[4])+
#         ggtitle(paste0('Global NPD per metric ton methane'))+
#         theme_minimal()+
#         theme(legend.position = 'none')+
#         theme(axis.text = element_text(size=16),
#               axis.title = element_text(size=16))+
#         geom_text(data=means, 
#             aes(y=means, x=discount.rate, group=discount.rate, 
#                 label=paste0('$', round(means, 2)), vjust=-1.5),
#             #position = position_dodge(1.3),
#             color    = 'grey20',
#             size     = 4) 
#         #scale_x_continuous(breaks=seq(2020,2100,10))
#         #scale_y_continuous(limits=c(0,11500))
# p1
# 
# ggsave(plot = p1, filename = 
#          file.path(Results,'Global BenMAP WebTool','Plots','Global_NPD_by_discounting.png'),width = 10,height = 5)

```
## Figure 3

Tornado sensitivity plot
```{r tornado}

#create a tornado plot with npd results from:
#1. different GCMs (created from monetization code?)
#2. BenMAP (created from monetization code?)
#3. Discounting (created from monetization code)
#3. BenMAP socioeconomic scenarios (from methane-ozone RFT)
#4. NOx (**)

#Read in 
Plots <- file.path(getwd(), 'analysis','Manuscript','Plots')
inputs <- file.path(getwd(),'analysis','Manuscript','BenMAP','Outputs')
rft_inputs <- file.path(getwd(),'output','npd')

Results <- file.path('Results')
globalresults <-
  read_csv(file.path(inputs,"npd_global_damage_transformation_woutCessation.csv"),
           col_types = cols())
Results2 <- file.path(rft_inputs,'npd_global_rff_means_NOx_1_MMM.csv')
rft_results <- read_csv(Results2, col_types = cols())
nox_results1 <- file.path(rft_inputs,'npd_global_rff_means_NOx_1_MMM.csv')
nox_results1 <- read_csv(nox_results1, col_types = cols())%>%
  mutate(NOx = '1')
nox_results5 <- file.path(rft_inputs, 'npd_global_rff_means_NOx_0.5_MMM.csv')
nox_results5 <- read_csv(nox_results5, col_types = cols())%>%
  mutate(NOx = '0.5')
nox_results15 <- file.path(rft_inputs, 'npd_global_rff_means_NOx_1.5_MMM.csv')
nox_results15 <- read_csv(nox_results15, col_types = cols()) %>%
  mutate(NOx = '1.5')
nox_total_results <- rbind(nox_results1,nox_results5,nox_results15)

@@

#calculate the absolute difference
val_col <- val_col - globalresults$mean[globalresults$Model=='MMM' & globalresults$discount.rate=='2.0% Ramsey']

@@

ggsave(plot = p1, filename = 
         file.path(Plots,'Fig3.png'),width = 10,height = 5)
